\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-05-30 doc/USER_MANUAL/authors.tex
fixed a typo in the users manual
added Masaru Nagaso as author, and added Windows installation information

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team: in alphabetical order,
Michael Afanasiev,
Jean-Paul (Pablo) Ampuero,
\'Etienne Bachmann,
Kangchen Bai,
Piero Basini,
C\'eline Blitz,
Alexis Bottero,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Paul Cristini,
Cl\'ement Durochat,
Percy Galvez,
Hom Nath Gharti,
Dominik G\"oddeke,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Youshan Liu,
David Luet,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Vadim Monteiller,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Kevin Pouget,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
James Smith,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Brice Videau,
Jean-Pierre Vilotte,
Zhinan Xie,
Chang-Hua Zhang,
Hejun Zhu.\\

@@

The code is released open-source under the GNU version 2+ license, see the license at the end of this manual.\\

>>>>

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team: in alphabetical order,
Michael Afanasiev,
Jean-Paul (Pablo) Ampuero,
\'Etienne Bachmann,
Kangchen Bai,
Piero Basini,
C\'eline Blitz,
Alexis Bottero,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Paul Cristini,
Cl\'ement Durochat,
Percy Galvez,
Hom Nath Gharti,
Dominik G\"oddeke,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Youshan Liu,
David Luet,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Vadim Monteiller,
Surendra Nadh Somala,
Masaru Nagaso,
Tarje Nissen-Meyer,
Daniel Peter,
Kevin Pouget,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
James Smith,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Brice Videau,
Jean-Pierre Vilotte,
Zhinan Xie,
Chang-Hua Zhang,
Hejun Zhu.\\

@@

The code is released open-source under the GNU version 3 license, see the license at the end of this manual.\\
